---
title: "Feature Transformation -- NGram (Transformer)"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_feature_ngram.R*

## ft_ngram

## Description
A feature transformer that converts the input array of strings into an array of n-grams. Null values in the input array are ignored. It returns an array of n-grams where each n-gram is represented by a space-separated string of words. 


## Usage
```r
ft_ngram( 
  x, 
  input_col = NULL, 
  output_col = NULL, 
  n = 2, 
  uid = random_string("ngram_"), 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `spark_connection`, `ml_pipeline`, or a `tbl_spark`. |
| input_col | The name of the input column. |
| output_col | The name of the output column. |
| n | Minimum n-gram length, greater than or equal to 1. Default: 2, bigram features |
| uid | A character string used to uniquely identify the feature transformer. |
| ... | Optional arguments; currently unused. |

## Details
When the input is empty, an empty array is returned. When the input array length is less than n (number of elements per n-gram), no n-grams are returned. 


## Value

The object returned depends on the class of `x`. 

  

- `spark_connection`: When `x` is a `spark_connection`, the function returns a `ml_transformer`,   a `ml_estimator`, or one of their subclasses. The object contains a pointer to   a Spark `Transformer` or `Estimator` object and can be used to compose   `Pipeline` objects. 

  

- `ml_pipeline`: When `x` is a `ml_pipeline`, the function returns a `ml_pipeline` with   the transformer or estimator appended to the pipeline. 

  

- `tbl_spark`: When `x` is a `tbl_spark`, a transformer is constructed then   immediately applied to the input `tbl_spark`, returning a `tbl_spark`



## See Also

See [https://spark.apache.org/docs/latest/ml-features.html](https://spark.apache.org/docs/latest/ml-features.html) for   more information on the set of transformations available for DataFrame   columns in Spark. 

Other feature transformers:  `ft_binarizer()`, `ft_bucketizer()`, `ft_chisq_selector()`, `ft_count_vectorizer()`, `ft_dct()`, `ft_elementwise_product()`, `ft_feature_hasher()`, `ft_hashing_tf()`, `ft_idf()`, `ft_imputer()`, `ft_index_to_string()`, `ft_interaction()`, `ft_lsh`, `ft_max_abs_scaler()`, `ft_min_max_scaler()`, `ft_normalizer()`, `ft_one_hot_encoder_estimator()`, `ft_one_hot_encoder()`, `ft_pca()`, `ft_polynomial_expansion()`, `ft_quantile_discretizer()`, `ft_r_formula()`, `ft_regex_tokenizer()`, `ft_robust_scaler()`, `ft_sql_transformer()`, `ft_standard_scaler()`, `ft_stop_words_remover()`, `ft_string_indexer()`, `ft_tokenizer()`, `ft_vector_assembler()`, `ft_vector_indexer()`, `ft_vector_slicer()`, `ft_word2vec()`


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
