---
title: "Feature Transformation -- PolynomialExpansion (Transformer)"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_feature_polynomial_expansion.R*

## ft_polynomial_expansion

## Description
 Perform feature expansion in a polynomial space. E.g. take a 2-variable feature   vector as an example: (x, y), if we want to expand it with degree 2, then   we get (x, x * x, y, x * y, y * y). 


## Usage
```r
 
ft_polynomial_expansion( 
  x, 
  input_col = NULL, 
  output_col = NULL, 
  degree = 2, 
  uid = random_string("polynomial_expansion_"), 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `spark_connection`, `ml_pipeline`, or a `tbl_spark`. |
| input_col | The name of the input column. |
| output_col | The name of the output column. |
| degree | The polynomial degree to expand, which should be greater than equal to 1. A value of 1 means no expansion. Default: 2 |
| uid | A character string used to uniquely identify the feature transformer. |
| ... | Optional arguments; currently unused. |



## Value
 The object returned depends on the class of `x`. If it is a `spark_connection`, the function returns a `ml_estimator` or a `ml_estimator` object. If it is a `ml_pipeline`, it will return a pipeline with the transformer or estimator appended to it. If a `tbl_spark`, it will return a `tbl_spark` with the transformation  applied to it. 



## See Also
 Other feature transformers:  `ft_binarizer()`, `ft_bucketizer()`, `ft_chisq_selector()`, `ft_count_vectorizer()`, `ft_dct()`, `ft_elementwise_product()`, `ft_feature_hasher()`, `ft_hashing_tf()`, `ft_idf()`, `ft_imputer()`, `ft_index_to_string()`, `ft_interaction()`, `ft_lsh`, `ft_max_abs_scaler()`, `ft_min_max_scaler()`, `ft_ngram()`, `ft_normalizer()`, `ft_one_hot_encoder()`, `ft_one_hot_encoder_estimator()`, `ft_pca()`, `ft_quantile_discretizer()`, `ft_r_formula()`, `ft_regex_tokenizer()`, `ft_robust_scaler()`, `ft_sql_transformer()`, `ft_standard_scaler()`, `ft_stop_words_remover()`, `ft_string_indexer()`, `ft_tokenizer()`, `ft_vector_assembler()`, `ft_vector_indexer()`, `ft_vector_slicer()`, `ft_word2vec()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
