---
title: "Feature Transformation -- RegexTokenizer (Transformer)"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_feature_regex_tokenizer.R*

## ft_regex_tokenizer

## Description
 A regex based tokenizer that extracts tokens either by using the provided regex pattern to split the text (default) or repeatedly matching the regex (if `gaps` is false). Optional parameters also allow filtering tokens using a minimal length. It returns an array of strings that can be empty. 


## Usage
```r
 
ft_regex_tokenizer( 
  x, 
  input_col = NULL, 
  output_col = NULL, 
  gaps = TRUE, 
  min_token_length = 1, 
  pattern = "\\s+", 
  to_lower_case = TRUE, 
  uid = random_string("regex_tokenizer_"), 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `spark_connection`, `ml_pipeline`, or a `tbl_spark`. |
| input_col | The name of the input column. |
| output_col | The name of the output column. |
| gaps | Indicates whether regex splits on gaps (TRUE) or matches tokens (FALSE). |
| min_token_length | Minimum token length, greater than or equal to 0. |
| pattern | The regular expression pattern to be used. |
| to_lower_case | Indicates whether to convert all characters to lowercase before tokenizing. |
| uid | A character string used to uniquely identify the feature transformer. |
| ... | Optional arguments; currently unused. |



## Value

 The object returned depends on the class of `x`.     

- `spark_connection`: When `x` is a `spark_connection`, the function returns a `ml_transformer`,   a `ml_estimator`, or one of their subclasses. The object contains a pointer to   a Spark `Transformer` or `Estimator` object and can be used to compose   `Pipeline` objects.    

- `ml_pipeline`: When `x` is a `ml_pipeline`, the function returns a `ml_pipeline` with   the transformer or estimator appended to the pipeline.    

- `tbl_spark`: When `x` is a `tbl_spark`, a transformer is constructed then   immediately applied to the input `tbl_spark`, returning a `tbl_spark` 

 



## See Also
 See [https://spark.apache.org/docs/latest/ml-features.html](https://spark.apache.org/docs/latest/ml-features.html) for   more information on the set of transformations available for DataFrame   columns in Spark.  Other feature transformers:  `ft_binarizer()`, `ft_bucketizer()`, `ft_chisq_selector()`, `ft_count_vectorizer()`, `ft_dct()`, `ft_elementwise_product()`, `ft_feature_hasher()`, `ft_hashing_tf()`, `ft_idf()`, `ft_imputer()`, `ft_index_to_string()`, `ft_interaction()`, `ft_lsh`, `ft_max_abs_scaler()`, `ft_min_max_scaler()`, `ft_ngram()`, `ft_normalizer()`, `ft_one_hot_encoder_estimator()`, `ft_one_hot_encoder()`, `ft_pca()`, `ft_polynomial_expansion()`, `ft_quantile_discretizer()`, `ft_r_formula()`, `ft_robust_scaler()`, `ft_sql_transformer()`, `ft_standard_scaler()`, `ft_stop_words_remover()`, `ft_string_indexer()`, `ft_tokenizer()`, `ft_vector_assembler()`, `ft_vector_indexer()`, `ft_vector_slicer()`, `ft_word2vec()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
