---
title: "Spark ML -- Transform, fit, and predict methods (ml_ interface)"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_transformation_methods.R*

## ml-transform-methods

## Description
Methods for transformation, fit, and prediction. These are mirrors of the corresponding sdf-transform-methods. 


## Usage
```r
is_ml_transformer(x) 

is_ml_estimator(x) 

ml_fit(x, dataset, ...) 

ml_transform(x, dataset, ...) 

ml_fit_and_transform(x, dataset, ...) 

ml_predict(x, dataset, ...) 

## S3 method for class 'ml_model_classification'
ml_predict(x, dataset, probability_prefix = "probability_", ...) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `ml_estimator`, `ml_transformer` (or a list thereof), or `ml_model` object. |
| dataset | A `tbl_spark`. |
| ... | Optional arguments; currently unused. |
| probability_prefix | String used to prepend the class probability output columns. |

## Details
These methods are 


## Value
When `x` is an estimator, `ml_fit()` returns a transformer whereas `ml_fit_and_transform()` returns a transformed dataset. When `x` is a transformer, `ml_transform()` and `ml_predict()` return a transformed dataset. When `ml_predict()` is called on a `ml_model` object, additional columns (e.g. probabilities in case of classification models) are appended to the transformed output for the user's convenience. 





```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
