---
title: "Compute correlation matrix"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_stat.R*

## ml_corr

## Description
 Compute correlation matrix 


## Usage
```r
 
ml_corr(x, columns = NULL, method = c("pearson", "spearman")) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `tbl_spark`. |
| columns | The names of the columns to calculate correlations of. If only one column is specified, it must be a vector column (for example, assembled using `ft_vector_assember()`). |
| method | The method to use, either `"pearson"` or `"spearman"`. |



## Value
 A correlation matrix organized as a data frame. 


## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
 
sc <- spark_connect(master = "local") 
iris_tbl <- sdf_copy_to(sc, iris, name = "iris_tbl", overwrite = TRUE) 
 
features <- c("Petal_Width", "Petal_Length", "Sepal_Length", "Sepal_Width") 
 
ml_corr(iris_tbl, columns = features, method = "pearson") 
 
```



```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
