---
title: "Default stop words"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_feature_stop_words_remover.R*

## ml_default_stop_words

## Description
 Loads the default stop words for the given language. 


## Usage
```r
 
ml_default_stop_words( 
  sc, 
  language = c("english", "danish", "dutch", "finnish", "french", "german", "hungarian", 
    "italian", "norwegian", "portuguese", "russian", "spanish", "swedish", "turkish"), 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| sc | A `spark_connection` |
| language | A character string. |
| ... | Optional arguments; currently unused. |

## Details
 Supported languages: danish, dutch, english, finnish, french,   german, hungarian, italian, norwegian, portuguese, russian, spanish,   swedish, turkish. Defaults to English. See [https://anoncvs.postgresql.org/cvsweb.cgi/pgsql/src/backend/snowball/stopwords/](https://anoncvs.postgresql.org/cvsweb.cgi/pgsql/src/backend/snowball/stopwords/)   for more details 


## Value
 A list of stop words. 



## See Also
 `ft_stop_words_remover` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
