---
title: "Spark ML -- Linear Regression"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_regression_linear_regression.R*

## ml_linear_regression

## Description
 Perform regression using linear regression. 


## Usage
```r
 
ml_linear_regression( 
  x, 
  formula = NULL, 
  fit_intercept = TRUE, 
  elastic_net_param = 0, 
  reg_param = 0, 
  max_iter = 100, 
  weight_col = NULL, 
  loss = "squaredError", 
  solver = "auto", 
  standardization = TRUE, 
  tol = 1e-06, 
  features_col = "features", 
  label_col = "label", 
  prediction_col = "prediction", 
  uid = random_string("linear_regression_"), 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `spark_connection`, `ml_pipeline`, or a `tbl_spark`. |
| formula | Used when `x` is a `tbl_spark`. R formula as a character string or a formula. This is used to transform the input dataframe before fitting, see ft_r_formula for details. |
| fit_intercept | Boolean; should the model be fit with an intercept term? |
| elastic_net_param | ElasticNet mixing parameter, in range [0, 1]. For alpha = 0, the penalty is an L2 penalty. For alpha = 1, it is an L1 penalty. |
| reg_param | Regularization parameter (aka lambda) |
| max_iter | The maximum number of iterations to use. |
| weight_col | The name of the column to use as weights for the model fit. |
| loss | The loss function to be optimized. Supported options: "squaredError" and "huber". Default: "squaredError" |
| solver | Solver algorithm for optimization. |
| standardization | Whether to standardize the training features before fitting the model. |
| tol | Param for the convergence tolerance for iterative algorithms. |
| features_col | Features column name, as a length-one character vector. The column should be single vector column of numeric values. Usually this column is output by `ft_r_formula`. |
| label_col | Label column name. The column should be a numeric column. Usually this column is output by `ft_r_formula`. |
| prediction_col | Prediction column name. |
| uid | A character string used to uniquely identify the ML estimator. |
| ... | Optional arguments; see Details. |



## Value
 The object returned depends on the class of `x`. If it is a `spark_connection`, the function returns a `ml_estimator` object. If it is a `ml_pipeline`, it will return a pipeline with the predictor appended to it. If a `tbl_spark`, it will return a `tbl_spark` with the predictions added to it. 


## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
 
sc <- spark_connect(master = "local") 
mtcars_tbl <- sdf_copy_to(sc, mtcars, name = "mtcars_tbl", overwrite = TRUE) 
 
partitions <- mtcars_tbl %>% 
  sdf_random_split(training = 0.7, test = 0.3, seed = 1111) 
 
mtcars_training <- partitions$training 
mtcars_test <- partitions$test 
 
lm_model <- mtcars_training %>% 
  ml_linear_regression(mpg ~ .) 
 
pred <- ml_predict(lm_model, mtcars_test) 
 
ml_regression_evaluator(pred, label_col = "mpg") 
 
```

## See Also
 Other ml algorithms:  `ml_aft_survival_regression()`, `ml_decision_tree_classifier()`, `ml_gbt_classifier()`, `ml_generalized_linear_regression()`, `ml_isotonic_regression()`, `ml_linear_svc()`, `ml_logistic_regression()`, `ml_multilayer_perceptron_classifier()`, `ml_naive_bayes()`, `ml_one_vs_rest()`, `ml_random_forest_classifier()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
