---
title: "Spark ML -- LinearSVC"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/ml_classification_linear_svc.R*

## ml_linear_svc

## Description
 Perform classification using linear support vector machines (SVM). This binary classifier optimizes the Hinge Loss using the OWLQN optimizer. Only supports L2 regularization currently. 


## Usage
```r
 
ml_linear_svc( 
  x, 
  formula = NULL, 
  fit_intercept = TRUE, 
  reg_param = 0, 
  max_iter = 100, 
  standardization = TRUE, 
  weight_col = NULL, 
  tol = 1e-06, 
  threshold = 0, 
  aggregation_depth = 2, 
  features_col = "features", 
  label_col = "label", 
  prediction_col = "prediction", 
  raw_prediction_col = "rawPrediction", 
  uid = random_string("linear_svc_"), 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A `spark_connection`, `ml_pipeline`, or a `tbl_spark`. |
| formula | Used when `x` is a `tbl_spark`. R formula as a character string or a formula. This is used to transform the input dataframe before fitting, see ft_r_formula for details. |
| fit_intercept | Boolean; should the model be fit with an intercept term? |
| reg_param | Regularization parameter (aka lambda) |
| max_iter | The maximum number of iterations to use. |
| standardization | Whether to standardize the training features before fitting the model. |
| weight_col | The name of the column to use as weights for the model fit. |
| tol | Param for the convergence tolerance for iterative algorithms. |
| threshold | in binary classification prediction, in range [0, 1]. |
| aggregation_depth | (Spark 2.1.0+) Suggested depth for treeAggregate (>= 2). |
| features_col | Features column name, as a length-one character vector. The column should be single vector column of numeric values. Usually this column is output by `ft_r_formula`. |
| label_col | Label column name. The column should be a numeric column. Usually this column is output by `ft_r_formula`. |
| prediction_col | Prediction column name. |
| raw_prediction_col | Raw prediction (a.k.a. confidence) column name. |
| uid | A character string used to uniquely identify the ML estimator. |
| ... | Optional arguments; see Details. |

## Details
 When `x` is a `tbl_spark` and `formula` (alternatively, `response` and `features`) is specified, the function returns a `ml_model` object wrapping a `ml_pipeline_model` which contains data pre-processing transformers, the ML predictor, and, for classification models, a post-processing transformer that converts predictions into class labels. For classification, an optional argument `predicted_label_col` (defaults to `"predicted_label"`) can be used to specify the name of the predicted label column. In addition to the fitted `ml_pipeline_model`, `ml_model` objects also contain a `ml_pipeline` object where the ML predictor stage is an estimator ready to be fit against data. This is utilized by `ml_save` with `type = "pipeline"` to faciliate model refresh workflows. 


## Value

 The object returned depends on the class of `x`.     

- `spark_connection`: When `x` is a `spark_connection`, the function returns an instance of a `ml_estimator` object. The object contains a pointer to   a Spark `Predictor` object and can be used to compose   `Pipeline` objects.    

- `ml_pipeline`: When `x` is a `ml_pipeline`, the function returns a `ml_pipeline` with   the predictor appended to the pipeline.    

- `tbl_spark`: When `x` is a `tbl_spark`, a predictor is constructed then   immediately fit with the input `tbl_spark`, returning a prediction model.    

- `tbl_spark`, with `formula`: specified When `formula`     is specified, the input `tbl_spark` is first transformed using a     `RFormula` transformer before being fit by     the predictor. The object returned in this case is a `ml_model` which is a     wrapper of a `ml_pipeline_model`. 

 


## Examples
```{r, eval=ecodown::examples_run()}
library(sparklyr)
 
```
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
 
library(dplyr) 
 
sc <- spark_connect(master = "local") 
iris_tbl <- sdf_copy_to(sc, iris, name = "iris_tbl", overwrite = TRUE) 
 
partitions <- iris_tbl %>% 
  filter(Species != "setosa") %>% 
  sdf_random_split(training = 0.7, test = 0.3, seed = 1111) 
 
iris_training <- partitions$training 
iris_test <- partitions$test 
 
svc_model <- iris_training %>% 
  ml_linear_svc(Species ~ .) 
 
pred <- ml_predict(svc_model, iris_test) 
 
ml_binary_classification_evaluator(pred) 
 
 
```

## See Also
 See [https://spark.apache.org/docs/latest/ml-classification-regression.html](https://spark.apache.org/docs/latest/ml-classification-regression.html) for   more information on the set of supervised learning algorithms.  Other ml algorithms:  `ml_aft_survival_regression()`, `ml_decision_tree_classifier()`, `ml_gbt_classifier()`, `ml_generalized_linear_regression()`, `ml_isotonic_regression()`, `ml_linear_regression()`, `ml_logistic_regression()`, `ml_multilayer_perceptron_classifier()`, `ml_naive_bayes()`, `ml_one_vs_rest()`, `ml_random_forest_classifier()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
