---
title: "Collect a Spark DataFrame into R."
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/sdf_wrapper.R*

## sdf_collect

## Description
Collects a Spark dataframe into R. 


## Usage
```r
sdf_collect(object, impl = c("row-wise", "row-wise-iter", "column-wise"), ...) 
```

## Arguments
|Arguments|Description|
|---|---|
| object | Spark dataframe to collect |
| impl | Which implementation to use while collecting Spark dataframe - row-wise: fetch the entire dataframe into memory and then process it row-by-row - row-wise-iter: iterate through the dataframe using RDD local iterator, processing one row at                  a time (hence reducing memory footprint) - column-wise: fetch the entire dataframe into memory and then process it column-by-column NOTE: (1) this will not apply to streaming or arrow use cases (2) this parameter will only affect implementation detail, and will not affect result of `sdf_collect`, and should only be set if performance profiling indicates any particular choice will be significantly better than the default choice ("row-wise") |
| ... | Additional options. |








```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
