---
title: "Write a Spark DataFrame to a CSV"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/data_interface.R*

## spark_write_csv

## Description
Write a Spark DataFrame to a tabular (typically, comma-separated) file. 


## Usage
```r
spark_write_csv( 
  x, 
  path, 
  header = TRUE, 
  delimiter = ",", 
  quote = "\"", 
  escape = "\\", 
  charset = "UTF-8", 
  null_value = NULL, 
  options = list(), 
  mode = NULL, 
  partition_by = NULL, 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A Spark DataFrame or dplyr operation |
| path | The path to the file. Needs to be accessible from the cluster. Supports the `"hdfs://"`, `"s3a://"` and `"file://"` protocols. |
| header | Should the first row of data be used as a header? Defaults to `TRUE`. |
| delimiter | The character used to delimit each column, defaults to `,`. |
| quote | The character used as a quote. Defaults to `'"'`. |
| escape | The character used to escape other characters, defaults to `\`. |
| charset | The character set, defaults to `"UTF-8"`. |
| null_value | The character to use for default values, defaults to `NULL`. |
| options | A list of strings with additional options. |
| mode | A `character` element. Specifies the behavior when data or   table already exists. Supported values include: 'error', 'append', 'overwrite' and   ignore. Notice that 'overwrite' will also change the column structure. <br>  For more details see also [https://spark.apache.org/docs/latest/sql-programming-guide.html#save-modes](https://spark.apache.org/docs/latest/sql-programming-guide.html#save-modes)<br>  for your version of Spark. |
| partition_by | A `character` vector. Partitions the output by the given columns on the file system. |
| ... | Optional arguments; currently unused. |






## See Also
Other Spark serialization routines:  `collect_from_rds()`, `spark_insert_table()`, `spark_load_table()`, `spark_read_avro()`, `spark_read_binary()`, `spark_read_csv()`, `spark_read_delta()`, `spark_read_image()`, `spark_read_jdbc()`, `spark_read_json()`, `spark_read_libsvm()`, `spark_read_orc()`, `spark_read_parquet()`, `spark_read_source()`, `spark_read_table()`, `spark_read_text()`, `spark_read()`, `spark_save_table()`, `spark_write_avro()`, `spark_write_delta()`, `spark_write_jdbc()`, `spark_write_json()`, `spark_write_orc()`, `spark_write_parquet()`, `spark_write_source()`, `spark_write_table()`, `spark_write_text()`


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
