---
title: "Retrieves or sets advisory size of the shuffle partition"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/spark_context_config.R*

## spark_advisory_shuffle_partition_size

## Description
 Retrieves or sets advisory size in bytes of the shuffle partition during adaptive optimization 


## Usage
```r
 
spark_advisory_shuffle_partition_size(sc, size = NULL) 
```

## Arguments
|Arguments|Description|
|---|---|
| sc | A `spark_connection`. |
| size | Advisory size in bytes of the shuffle partition. Defaults to `NULL` to retrieve configuration entries. |






## See Also
 Other Spark runtime configuration:  `spark_adaptive_query_execution()`, `spark_auto_broadcast_join_threshold()`, `spark_coalesce_initial_num_partitions()`, `spark_coalesce_min_num_partitions()`, `spark_coalesce_shuffle_partitions()`, `spark_session_config()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
