---
title: "Find a given Spark installation by version."
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/install_spark.R*

## spark_install_find

## Description
 Find a given Spark installation by version. 


## Usage
```r
 
spark_install_find( 
  version = NULL, 
  hadoop_version = NULL, 
  installed_only = TRUE, 
  latest = FALSE, 
  hint = FALSE 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| version | Version of Spark to install. See `spark_available_versions` for a list of supported versions |
| hadoop_version | Version of Hadoop to install. See `spark_available_versions` for a list of supported versions |
| installed_only | Search only the locally installed versions? |
| latest | Check for latest version? |
| hint | On failure should the installation code be provided? |








```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
