---
title: "Read from a generic source into a Spark DataFrame."
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/data_interface.R*

## spark_read_source

## Description
 Read from a generic source into a Spark DataFrame. 


## Usage
```r
 
spark_read_source( 
  sc, 
  name = NULL, 
  path = name, 
  source, 
  options = list(), 
  repartition = 0, 
  memory = TRUE, 
  overwrite = TRUE, 
  columns = NULL, 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| sc | A `spark_connection`. |
| name | The name to assign to the newly generated table. |
| path | The path to the file. Needs to be accessible from the cluster. Supports the `"hdfs://"`, `"s3a://"` and `"file://"` protocols. |
| source | A data source capable of reading data. |
| options | A list of strings with additional options. See [https://spark.apache.org/docs/latest/sql-programming-guide.html#configuration](https://spark.apache.org/docs/latest/sql-programming-guide.html#configuration). |
| repartition | The number of partitions used to distribute the generated table. Use 0 (the default) to avoid partitioning. |
| memory | Boolean; should the data be loaded eagerly into memory? (That is, should the table be cached?) |
| overwrite | Boolean; overwrite the table with the given name if it already exists? |
| columns | A vector of column names or a named vector of column types. If specified, the elements can be `"binary"` for `BinaryType`, `"boolean"` for `BooleanType`, `"byte"` for `ByteType`, `"integer"` for `IntegerType`, `"integer64"` for `LongType`, `"double"` for `DoubleType`, `"character"` for `StringType`, `"timestamp"` for `TimestampType` and `"date"` for `DateType`. |
| ... | Optional arguments; currently unused. |






## See Also
 Other Spark serialization routines:  `collect_from_rds()`, `spark_insert_table()`, `spark_load_table()`, `spark_read()`, `spark_read_avro()`, `spark_read_binary()`, `spark_read_csv()`, `spark_read_delta()`, `spark_read_image()`, `spark_read_jdbc()`, `spark_read_json()`, `spark_read_libsvm()`, `spark_read_orc()`, `spark_read_parquet()`, `spark_read_table()`, `spark_read_text()`, `spark_save_table()`, `spark_write_avro()`, `spark_write_csv()`, `spark_write_delta()`, `spark_write_jdbc()`, `spark_write_json()`, `spark_write_orc()`, `spark_write_parquet()`, `spark_write_source()`, `spark_write_table()`, `spark_write_text()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
