---
title: "Set of functions to provide integration with the RStudio IDE"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/spark_ide.R*

## spark_ide_connection_open

## Description
 Set of functions to provide integration with the RStudio IDE 


## Usage
```r
 
spark_ide_connection_open(con, env, connect_call) 
 
spark_ide_connection_closed(con) 
 
spark_ide_connection_updated(con, hint) 
 
spark_ide_connection_actions(con) 
 
spark_ide_objects(con, catalog, schema, name, type) 
 
spark_ide_columns( 
  con, 
  table = NULL, 
  view = NULL, 
  catalog = NULL, 
  schema = NULL 
) 
 
spark_ide_preview( 
  con, 
  rowLimit, 
  table = NULL, 
  view = NULL, 
  catalog = NULL, 
  schema = NULL 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| con | Valid Spark connection |
| env | R environment of the interactive R session |
| connect_call | R code that can be used to re-connect to the Spark connection |
| hint | Name of the Spark connection that the RStudio IDE can use as reference. |
| catalog | Name of the top level of the requested table or view |
| schema | Name of the second most top level of the requested level or view |
| name | The new of the view or table being requested |
| type | Type of the object being requested, 'view' or 'table' |
| table | Name of the requested table |
| view | Name of the requested view |
| rowLimit | The number of rows to show in the 'Preview' pane of the RStudio IDE |

## Details
 These function are meant for downstream packages, that provide additional backends to `sparklyr`, to override the opening, closing, update, and preview functionality. The arguments are driven by what the RStudio IDE API expects them to be, so this is the reason why some use `type` to designated views or tables, and others have one argument for `table`, and another for `view`. 







```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
