---
title: "Write files to the stream"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_data.R*

## stream_write_csv

## Description
 Write files to the stream 


## Usage
```r
 
stream_write_csv( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path(path, "checkpoint"), 
  header = TRUE, 
  delimiter = ",", 
  quote = "\"", 
  escape = "\\", 
  charset = "UTF-8", 
  null_value = NULL, 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_text( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path(path, "checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_json( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path(path, "checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_parquet( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path(path, "checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_orc( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path(path, "checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_kafka( 
  x, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path("checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_console( 
  x, 
  mode = c("append", "complete", "update"), 
  options = list(), 
  trigger = stream_trigger_interval(), 
  partition_by = NULL, 
  ... 
) 
 
stream_write_delta( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  checkpoint = file.path("checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A Spark DataFrame or dplyr operation |
| path | The path to the file. Needs to be accessible from the cluster. Supports the `"hdfs://"`, `"s3a://"` and `"file://"` protocols. |
| mode | Specifies how data is written to a streaming sink. Valid values are `"append"`, `"complete"` or `"update"`. |
| trigger | The trigger for the stream query, defaults to micro-batches running every 5 seconds. See `stream_trigger_interval` and   `stream_trigger_continuous`. |
| checkpoint | The location where the system will write all the checkpoint information to guarantee end-to-end fault-tolerance. |
| header | Should the first row of data be used as a header? Defaults to `TRUE`. |
| delimiter | The character used to delimit each column, defaults to `,`. |
| quote | The character used as a quote. Defaults to `'"'`. |
| escape | The character used to escape other characters, defaults to `\`. |
| charset | The character set, defaults to `"UTF-8"`. |
| null_value | The character to use for default values, defaults to `NULL`. |
| options | A list of strings with additional options. |
| partition_by | Partitions the output by the given list of columns. |
| ... | Optional arguments; currently unused. |





## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
 
 
sc <- spark_connect(master = "local") 
 
dir.create("csv-in") 
write.csv(iris, "csv-in/data.csv", row.names = FALSE) 
 
csv_path <- file.path("file://", getwd(), "csv-in") 
 
stream <- stream_read_csv(sc, csv_path) %>% stream_write_csv("csv-out") 
 
stream_stop(stream) 
 
 
```

## See Also
 Other Spark stream serialization:  `stream_write_memory()`, `stream_write_table()` 


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
