---
title: "Stream Statistics"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_view.R*

## stream_stats

## Description
 Collects streaming statistics, usually, to be used with `stream_render()` to render streaming statistics. 


## Usage
```r
 
stream_stats(stream, stats = list()) 
```

## Arguments
|Arguments|Description|
|---|---|
| stream | The stream to collect statistics from. |
| stats | An optional stats object generated using `stream_stats()`. |



## Value
 A stats object containing streaming statistics that can be passed   back to the `stats` parameter to continue aggregating streaming stats. 


## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
 
sc <- spark_connect(master = "local") 
sdf_len(sc, 10) %>% 
  spark_write_parquet(path = "parquet-in") 
 
stream <- stream_read_parquet(sc, "parquet-in") %>% 
  stream_write_parquet("parquet-out") 
 
stream_stats(stream) 
 
 
```



```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
