---
title: "Render Stream"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_view.R*

## stream_render

## Description
 Collects streaming statistics to render the stream as an 'htmlwidget'. 


## Usage
```r
 
stream_render(stream = NULL, collect = 10, stats = NULL, ...) 
```

## Arguments
|Arguments|Description|
|---|---|
| stream | The stream to render |
| collect | The interval in seconds to collect data before rendering the 'htmlwidget'. |
| stats | Optional stream statistics collected using `stream_stats()`, when specified, `stream` should be omitted. |
| ... | Additional optional arguments. |





## Examples
```{r, eval=ecodown::examples_not_run()}
 
library(sparklyr) 
sc <- spark_connect(master = "local") 
 
dir.create("iris-in") 
write.csv(iris, "iris-in/iris.csv", row.names = FALSE) 
 
stream <- stream_read_csv(sc, "iris-in/") %>% 
  stream_write_csv("iris-out/") 
 
stream_render(stream) 
stream_stop(stream) 
 
```



```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
