---
title: "Read Delta Stream"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_data.R*

## stream_read_delta

## Description
Reads a Delta Lake table as a Spark dataframe stream. 


## Usage
```r
stream_read_delta(sc, path, name = NULL, options = list(), ...) 
```

## Arguments
|Arguments|Description|
|---|---|
| sc | A `spark_connection`. |
| path | The path to the file. Needs to be accessible from the cluster. Supports the `"hdfs://"`, `"s3a://"` and `"file://"` protocols. |
| name | The name to assign to the newly generated stream. |
| options | A list of strings with additional options. |
| ... | Optional arguments; currently unused. |

## Details
Please note that Delta Lake requires installing the appropriate package by setting the `packages` parameter to `"delta"` in `spark_connect()`




## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr) 
sc <- spark_connect(master = "local", version = "2.4.0", packages = "delta") 
sdf_len(sc, 5) %>% spark_write_delta(path = "delta-test") 
stream <- stream_read_delta(sc, "delta-test") %>% 
  stream_write_json("json-out") 
stream_stop(stream) 
```

## See Also
Other Spark stream serialization:  `stream_read_csv()`, `stream_read_json()`, `stream_read_kafka()`, `stream_read_orc()`, `stream_read_parquet()`, `stream_read_socket()`, `stream_read_text()`, `stream_write_console()`, `stream_write_csv()`, `stream_write_delta()`, `stream_write_json()`, `stream_write_kafka()`, `stream_write_memory()`, `stream_write_orc()`, `stream_write_parquet()`, `stream_write_text()`


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
