---
title: "Read JSON Stream"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_data.R*

## stream_read_json

## Description
Reads a JSON stream as a Spark dataframe stream. 


## Usage
```r
stream_read_json(sc, path, name = NULL, columns = NULL, options = list(), ...) 
```

## Arguments
|Arguments|Description|
|---|---|
| sc | A `spark_connection`. |
| path | The path to the file. Needs to be accessible from the cluster. Supports the `"hdfs://"`, `"s3a://"` and `"file://"` protocols. |
| name | The name to assign to the newly generated stream. |
| columns | A vector of column names or a named vector of column types. If specified, the elements can be `"binary"` for `BinaryType`, `"boolean"` for `BooleanType`, `"byte"` for `ByteType`, `"integer"` for `IntegerType`, `"integer64"` for `LongType`, `"double"` for `DoubleType`, `"character"` for `StringType`, `"timestamp"` for `TimestampType` and `"date"` for `DateType`. |
| options | A list of strings with additional options. |
| ... | Optional arguments; currently unused. |





## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
sc <- spark_connect(master = "local") 
dir.create("json-in") 
jsonlite::write_json(list(a = c(1, 2), b = c(10, 20)), "json-in/data.json") 
json_path <- file.path("file://", getwd(), "json-in") 
stream <- stream_read_json(sc, json_path) %>% stream_write_json("json-out") 
stream_stop(stream) 
```

## See Also
Other Spark stream serialization:  `stream_read_csv()`, `stream_read_delta()`, `stream_read_kafka()`, `stream_read_orc()`, `stream_read_parquet()`, `stream_read_socket()`, `stream_read_text()`, `stream_write_console()`, `stream_write_csv()`, `stream_write_delta()`, `stream_write_json()`, `stream_write_kafka()`, `stream_write_memory()`, `stream_write_orc()`, `stream_write_parquet()`, `stream_write_text()`


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
