---
title: "Generate Test Stream"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_operations.R*

## stream_generate_test

## Description
 Generates a local test stream, useful when testing streams locally. 


## Usage
```r
 
stream_generate_test( 
  df = rep(1:1000), 
  path = "source", 
  distribution = floor(10 + 1e+05 * stats::dbinom(1:20, 20, 0.5)), 
  iterations = 50, 
  interval = 1 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| df | The data frame used as a source of rows to the stream, will be cast to data frame if needed. Defaults to a sequence of one thousand entries. |
| path | Path to save stream of files to, defaults to `"source"`. |
| distribution | The distribution of rows to use over each iteration, defaults to a binomial distribution. The stream will cycle through the distribution if needed. |
| iterations | Number of iterations to execute before stopping, defaults to fifty. |
| interval | The inverval in seconds use to write the stream, defaults to one second. |

## Details
 This function requires the `callr` package to be installed. 







```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
