---
title: "Write JSON Stream"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/stream_data.R*

## stream_write_json

## Description
Writes a Spark dataframe stream into a JSON stream. 


## Usage
```r
stream_write_json( 
  x, 
  path, 
  mode = c("append", "complete", "update"), 
  trigger = stream_trigger_interval(), 
  checkpoint = file.path(path, "checkpoints", random_string("")), 
  options = list(), 
  partition_by = NULL, 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| x | A Spark DataFrame or dplyr operation |
| path | The destination path. Needs to be accessible from the cluster. Supports the `"hdfs://"`, `"s3a://"` and `"file://"` protocols. |
| mode | Specifies how data is written to a streaming sink. Valid values are `"append"`, `"complete"` or `"update"`. |
| trigger | The trigger for the stream query, defaults to micro-batches runnnig every 5 seconds. See `stream_trigger_interval` and `stream_trigger_continuous`. |
| checkpoint | The location where the system will write all the checkpoint information to guarantee end-to-end fault-tolerance. |
| options | A list of strings with additional options. |
| partition_by | Partitions the output by the given list of columns. |
| ... | Optional arguments; currently unused. |





## Examples
```{r, eval=ecodown::examples_not_run()}
library(sparklyr)
sc <- spark_connect(master = "local") 
dir.create("json-in") 
jsonlite::write_json(list(a = c(1, 2), b = c(10, 20)), "json-in/data.json") 
json_path <- file.path("file://", getwd(), "json-in") 
stream <- stream_read_json(sc, json_path) %>% stream_write_json("json-out") 
stream_stop(stream) 
```

## See Also
Other Spark stream serialization:  `stream_read_csv()`, `stream_read_delta()`, `stream_read_json()`, `stream_read_kafka()`, `stream_read_orc()`, `stream_read_parquet()`, `stream_read_socket()`, `stream_read_text()`, `stream_write_console()`, `stream_write_csv()`, `stream_write_delta()`, `stream_write_kafka()`, `stream_write_memory()`, `stream_write_orc()`, `stream_write_parquet()`, `stream_write_text()`


```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
