---
title: "Manipulating data with dplyr"
---
<!-- Introduction:Docs/concepts/motivating example
Filtering
Aggregation
Sampling/Windowing
Table Caching-->

<!--sparklyr is an R package that provides a frontend to use Apache Spark from R. sparklyr provides a distributed data frame implementation that supports operations like selection, filtering, aggregation etc. (similar to R data frames, dplyr) but on large datasets. SparkR also supports distributed machine learning using MLlib.-->

<!--A DataFrame is a distributed collection of data organized into named columns. It is conceptually equivalent to a table in a relational database or a data frame in R, but with richer optimizations under the hood. DataFrames can be constructed from a wide array of sources such as: structured data files, tables in Hive, external databases, or existing local R data frames.-->


```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```


# Overview

`dplyr` is an R package for working with structured data both in and outside of R. `dplyr` makes data manipulation for R users easy, consistent, and high performant. You can load `dplyr` by running:

```{r, eval = FALSE}
library("dplyr")
```

Use `dplyr` as your main interface for manipulating Spark dataframes. It gives you the ability to:

* [Operate on a DataFrame (select, filter, aggregate, etc.)](#operate-on-a-dataframe)
* [Use window functions](#use-window-functions)
* [Join DataFrames](#join-dataframes)
* [Sample data](#sample-data)
* [Cache a DataFrame](#cache-a-dataframe)

Statements in `dplyr` can be chained together using pipes defined by the [magrittr](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html) R package. `dplyr` also supports [non-standard evalution](https://cran.r-project.org/web/packages/dplyr/vignettes/nse.html) of its arguments. For more information on `dplyr`, see the [introduction](https://cran.r-project.org/web/packages/dplyr/vignettes/introduction.html), a guide for connecting to [databases](https://cran.r-project.org/web/packages/dplyr/vignettes/databases.html), and a variety of [vignettes](https://cran.r-project.org/web/packages/dplyr/index.html).

# Setup and example data

To explore the basic data manipulation verbs of dplyr, we'll start with data stored in the `nycflights13` R package. This package contains data for all 336,776 flights departing New York City in 2013. It also includes useful metadata on airlines, airports, weather, and planes. The data comes from the US [Bureau of Transportation Statistics](http://www.transtats.bts.gov/DatabaseInfo.asp?DB_ID=120&Link=0), and is documented in `?nycflights13`

Connect to the cluster and copy the flights data using the `copy_to` function. Caveat: The flight data in `nycflights13` is convenient for `dplyr` demonstrations because it is small, but in practice large data will rarely be copied directly from R objects. 




```{r message=FALSE, warning=FALSE}
library(sparklyr)
library(nycflights13)
sc <- spark_connect()
flights <- copy_to(sc, nycflights13::flights, "flights")
src_tbls(sc)
```

# Operate on a DataFrame

## dplyr Verbs

Verbs are `dplyr` commands for manipulating data. When connected to a Spark DataFrame, dplyr translates the commands into Spark SQL statements. Remote data sources use exactly the same five verbs as local data sources. Here are the five verbs with their corresponding SQL commands:

* `select` ~ `SELECT`
* `filter` ~ `WHERE`
* `arrange` ~ `ORDER`
* `mutate` ~ `operator (+, *, log, etc.)`
* `summarise` ~ `aggregator (sum, min, sd, etc.)`

```{r}
select(flights, year:day, dep_delay, arr_delay)
filter(flights, dep_delay > 240)
arrange(flights, year, month, day)
mutate(flights, speed = air_time / distance)
summarise(flights, delay = mean(dep_time))
```

## Laziness

When working with databases, dplyr tries to be as lazy as possible:

* It never pulls data into R unless you explicitly ask for it.

* It delays doing any work until the last possible moment: it collects together
  everything you want to do and then sends it to the database in one step.

For example, take the following code:

```{r}
c1 <- filter(flights, year == 2013, month == 1, day == 1)
c2 <- filter(c1, carrier %in% c('UA', 'WN', 'AA', 'DL'), air_time > 0)
c3 <- select(c2, year, month, day, carrier, dep_delay, air_time, distance)
c4 <- mutate(c3, speed = distance / air_time * 60)
c5 <- arrange(c4, year, month, day, carrier)
```

Suprisingly, this sequence of operations never actually touches the database. It's not until you ask for the data (e.g. by printing `c4`) that dplyr generates the SQL and requests the results from the database. Even then it only pulls down 10 rows.

```{r}
c4
```

## Collect, compute, collapse

You can copy data from Spark into R's memory by using `collect()`. `collect()` executes the Spark query and returns the results to R for further analysis and visualization.

```{r, eval = FALSE}
library(ggplot2)
carrierspeed <- collect(c4)
with(carrierspeed, pairwise.t.test(speed, carrier))
ggplot(carrierspeed, aes(carrier, speed)) + geom_boxplot()
```

If you want to execute a query and store the results in a temporary table, use `compute()`

```{r, eval = FALSE}
compute(c4, 'carrierspeed')
src_tbls(sc)
```

Finally, you can use `collapse()` to turn the query into a table expression.

## Chaining commands via pipes

You can use pipes to write cleaner syntax. Using the same example from above, you can write a much cleaner version like this:

```{r, eval = FALSE}
flights %>%
  filter(year == 2013, month == 1, day == 1) %>%
  select(year, month, day, carrier, dep_delay, air_time, distance) %>%
  mutate(speed = distance / air_time * 60) %>%
  arrange(year, month, day, carrier)
```

## Grouping

The `group_by` function corresponds to the `GROUP BY` statement in SQL.

```{r}
flights %>%
  group_by(tailnum) %>%
  summarize(count = n(), dist = mean(distance), delay = mean(arr_delay)) %>%
  filter(count > 20, dist < 2000)
```

## Translate SQL

dplyr knows how to convert the following R functions to Spark SQL:

```{r, eval = FALSE}
+, -, *, /, %%, ^
abs, acos, acosh, asin, asinh, atan, atan2, atanh, ceiling, cos, cosh, cot, coth, exp, floor, log, log10, round, sign, sin, sinh, sqrt, tan, tanh
<, <=, !=, >=, >, ==, %in%
&, &&, |, ||, !, xor
mean, sum, min, max, sd, var
```
*Verify which are supported in Spark SQL*


# Use window functions

`dplyr` supports Spark SQL window functions. Window functions are used in conjunction with mutate and filter to solve a wide range of problems. You can compare the `dplyr` syntax to the query it has generated by using `sql_render()`.

```{r, collapse=TRUE}
# Find the most and least delayed flight each day
bestworst <- flights %>%
  group_by(year, month, day)
  select(arr_delay) %>% 
  filter(arr_delay == min(arr_delay) || arr_delay == max(arr_delay))
sql_render(bestworst)

# Rank each flight within a daily
ranked <- flights %>%
  group_by(year, month, day) %>%
  select(arr_delay) %>% 
  mutate(rank = rank(desc(arr_delay)))
sql_render(ranked)
```


# Join DataFrames

It's rare that a data analysis involves only a single table of data. In practice, you'll normally have many tables that contribute to an analysis, and you need flexible tools to combine them. In dplyr, there are three families of verbs that work with two tables at a time:

* Mutating joins, which add new variables to one table from matching rows in 
  another.

* Filtering joins, which filter observations from one table based on whether or 
  not they match an observation in the other table.

* Set operations, which combine the observations in the data sets as if they 
  were set elements.

All two-table verbs work similarly. The first two arguments are `x` and `y`, and provide the tables to combine. The output is always a new table with the same type as `x`.


```{r, eval=FALSE}
airlines <- copy_to(sc, nycflights13::airlines, "airlines")
flights %>% left_join(airlines)
sql_render(flights %>% left_join(airlines))
tbl(sc, sql('select * from flights a left outer join airlines b on (a.carrier = b.carrier)'))
```


# Sample data

You can use `sample_n()` and `sample_frac()` to take a random sample of rows: use `sample_n()` for a fixed number and `sample_frac()` for a fixed fraction.

```{r}
sample_n(flights, 10)
sample_frac(flights, 0.01)
```


# Cache a DataFrame

You can cache and unchace DataFrames with `tbl_cache()` and `tbl_uncache()`. Caching DataFrames forces them into memory, improving query performance.

```{r message=FALSE, warning=FALSE}
tbl_cache(sc, 'flights')
tbl_uncache(sc, 'flights')
```
