---
title: "Get Started"
format:
  html:
    theme: default
    toc: true
execute:
  eval: false
---

```{r, include = FALSE}
library(sparklyr) 
library(dplyr)
```


::: {.panel-tabset}

## Installation

You can install the `sparklyr` package from [CRAN](https://CRAN.r-project.org) as follows:

```{r}
#| eval: false

install.packages("sparklyr")
```

You should also install a local version of Spark for development purposes. **This step is only necessary if you do not have a Spark cluster to experiment with**:

```{r}
#| eval: false

library(sparklyr)

spark_install()
```

### Connecting to Spark

You can connect to both local instances of Spark as well as remote Spark clusters. Here we'll connect to a local instance of Spark via the `spark_connect()` function:

```{r}
#| eval: false

library(sparklyr)

sc <- spark_connect(master = "local")
```


The returned Spark connection (`sc`) provides a remote dplyr data source to the Spark cluster.

For more information on connecting to remote Spark clusters see the [Deployment](https://spark.rstudio.com/deployment.html) section of the `sparklyr` website.

## Manipulate Data

```{r}
library(sparklyr)
sc <- spark_connect(master = "local")
flights_tbl <- copy_to(sc, nycflights13::flights, "spark_flights")
```

### Using `dplyr`

We can now use all of the available dplyr verbs against the tables within the cluster.

We'll start by copying some data sets from R into the Spark cluster (note that you may need to install the `nycflights13`):

To start with here's a simple filtering example:

```{r}
library(dplyr)

flights_tbl %>% 
  filter(dep_delay == 2) %>% 
  select(carrier, sched_dep_time, dep_time, dep_delay) %>% 
  head(5)
```


[Introduction to `dplyr`](https://CRAN.R-project.org/package=dplyr) provides additional `dplyr` examples you can try. For example, consider the last example from the tutorial which plots data on flight delays:

```{r}
delay <- flights_tbl %>%
  group_by(tailnum) %>%
  summarise(
    count = n(), 
    dist = mean(distance, na.rm = TRUE), 
    delay = mean(arr_delay, na.rm = TRUE)
    ) %>%
  filter(count > 20, dist < 2000, !is.na(delay)) 

show_query(delay)
```


```{r}
#| message: false
#| fig-width: 4
#| fig-height: 3

library(ggplot2)

delay %>%
  collect() %>%  # Downloads the data into R
  ggplot(aes(dist, delay)) +
  geom_point(aes(size = count), alpha = 1/2) +
  geom_smooth() +
  scale_size_area(max_size = 2)
```

For additional documentation on using dplyr with Spark see the [dplyr](https://spark.rstudio.com/dplyr.html) section of the sparklyr website.

### Using SQL

It's also possible to execute SQL queries directly against tables within a Spark cluster. The `spark_connection()` object implements a [DBI](https://github.com/rstats-db/DBI) interface for Spark, so you can use `dbGetQuery()` to execute SQL and return the result as an R data frame:

```{r sql-dbi}
library(DBI)

dbGetQuery(sc, "SELECT carrier, sched_dep_time, dep_time, dep_delay FROM spark_flights LIMIT 5")

```
```{r}
spark_disconnect(sc)
```


## Machine Learning

You can orchestrate machine learning algorithms in a Spark cluster via the [machine learning](https://spark.apache.org/docs/latest/mllib-guide.html) functions within **sparklyr**. These functions connect to a set of high-level APIs built on top of DataFrames that help you create and tune machine learning workflows.

Here's an example where we use [ml_linear_regression](https://spark.rstudio.com/reference/ml_linear_regression/) to fit a linear regression model. We'll use the built-in `mtcars` dataset, and see if we can predict a car's fuel consumption (`mpg`) based on its weight (`wt`), and the number of cylinders the engine contains (`cyl`). We'll assume in each case that the relationship between `mpg` and each of our features is linear.

```{r}
#| eval: false

# copy mtcars into spark
mtcars_tbl <- copy_to(sc, mtcars, overwrite = TRUE)

# transform our data set, and then partition into 'training', 'test'
partitions <- mtcars_tbl %>%
  filter(hp >= 100) %>%
  mutate(cyl8 = cyl == 8) %>%
  sdf_partition(training = 0.5, test = 0.5, seed = 1099)

# fit a linear model to the training dataset
fit <- partitions$training %>%
  ml_linear_regression(response = "mpg", features = c("wt", "cyl"))
fit
```

For linear regression models produced by Spark, we can use `summary()` to learn a bit more about the quality of our fit, and the statistical significance of each of our predictors.

```{r}
#| eval: false

summary(fit)
```

Spark machine learning supports a wide array of algorithms and feature transformations and as illustrated above it's easy to chain these functions together with dplyr pipelines. To learn more see the [machine learning](https://spark.rstudio.com/mlib/) section.

## Reading and Writing Data

You can read and write data in CSV, JSON, and Parquet formats. Data can be stored in HDFS, S3, or on the local filesystem of cluster nodes.

```{r}
#| eval: false

temp_csv <- tempfile(fileext = ".csv")
temp_parquet <- tempfile(fileext = ".parquet")
temp_json <- tempfile(fileext = ".json")

spark_write_csv(iris_tbl, temp_csv)
iris_csv_tbl <- spark_read_csv(sc, "iris_csv", temp_csv)

spark_write_parquet(iris_tbl, temp_parquet)
iris_parquet_tbl <- spark_read_parquet(sc, "iris_parquet", temp_parquet)

spark_write_json(iris_tbl, temp_json)
iris_json_tbl <- spark_read_json(sc, "iris_json", temp_json)

src_tbls(sc)
```

:::