---
title: "R interface for GraphFrames"
output:
  html_document:
    toc_depth: 2
    fig_width: 9
    fig_height: 5
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(warning = FALSE)
#knitr::opts_chunk$set(fig.path = "tools/readme/", dev = "png")
```

## Highlights

- Support for [GraphFrames](https://graphframes.github.io/) which aims to provide the functionality of [GraphX](http://spark.apache.org/graphx/).
- Perform graph algorithms like: [PageRank](https://graphframes.github.io/api/scala/index.html#org.graphframes.lib.PageRank), [ShortestPaths](https://graphframes.github.io/api/scala/index.html#org.graphframes.lib.ShortestPaths) and many [others](https://graphframes.github.io/api/scala/#package).
- Designed to work with [sparklyr](https://spark.rstudio.com) and the [sparklyr extensions](http://spark.rstudio.com/extensions.html).


## Installation

To install from CRAN, run:
```{r eval=FALSE}
install.packages("graphframes")
```

For the development version, run:
```{r eval=FALSE}
devtools::install_github("rstudio/graphframes")
```

## Examples

The examples make use of the `highschool` dataset from the `ggplot` package.

### Create a GraphFrame

The base for graph analyses in Spark, using `sparklyr`, will be a GraphFrame.  

Open a new Spark connection using `sparklyr`, and copy the `highschool` data set

```{r message=FALSE}
library(graphframes)
library(sparklyr)
library(dplyr)

sc <- spark_connect(master = "local", version = "2.1.0")

highschool_tbl <- copy_to(sc, ggraph::highschool, "highschool")

head(highschool_tbl)
```

The vertices table is be constructed using `dplyr`.  The variable name expected by the GraphFrame is **id**.

```{r message=FALSE}

from_tbl <- highschool_tbl %>% 
  distinct(from) %>% 
  transmute(id = from)

to_tbl <- highschool_tbl %>% 
  distinct(to) %>% 
  transmute(id = to)
  
  
vertices_tbl <- from_tbl %>%
  sdf_bind_rows(to_tbl)

head(vertices_tbl)
```

The edges table can also be created using `dplyr`. In order for the GraphFrame to work,  the **from** variable needs be renamed **src**, and the **to** variable **dst**.
```{r message=FALSE}
# Create a table with <source, destination> edges
edges_tbl <- highschool_tbl %>% 
  transmute(src = from, dst = to)
```

The `gf_graphframe()` function creates a new GraphFrame 
```{r message=FALSE}
gf_graphframe(vertices_tbl, edges_tbl) 
```

### Basic Page Rank

We will calculate [PageRank](https://en.wikipedia.org/wiki/PageRank) over this dataset. The `gf_graphframe()` command can easily be piped into the `gf_pagerank()` function to execute the Page Rank.
```{r message=FALSE}
gf_graphframe(vertices_tbl, edges_tbl) %>%
  gf_pagerank(reset_prob = 0.15, max_iter = 10L, source_id = "1")
```


Additionaly, one can calculate the degrees of vertices using `gf_degrees` as follows:

```{r message=FALSE}
gf_graphframe(vertices_tbl, edges_tbl) %>% 
  gf_degrees()
```

### Visualizations

In order to visualize large `graphframe`s, one can use `sample_n` and then use `ggraph` with `igraph` to visualize the graph as follows:

```{r message=FALSE}
library(ggraph)
library(igraph)

graph <- highschool_tbl %>%
  sample_n(20) %>%
  collect() %>%
  graph_from_data_frame()

ggraph(graph, layout = 'kk') + 
    geom_edge_link(aes(colour = factor(year))) + 
    geom_node_point() + 
    ggtitle('An example')
```


## Additional functions

Apart from calculating `PageRank` using `gf_pagerank`, the following functions are available: 

- `gf_bfs()`: Breadth-first search (BFS).
- `gf_connected_components()`: Connected components.
- `gf_shortest_paths()`: Shortest paths algorithm.
- `gf_scc()`: Strongly connected components.
- `gf_triangle_count`: Computes the number of triangles passing through each vertex and others.


```{r, include = FALSE}
spark_disconnect(sc)
```