---
title: "Writes the 'requirements.txt' file, containing the needed Python libraries"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/python-requirements.R*

## requirements_write

## Description
 This is a helper function that it is meant to be used for deployments of the document or application. By default, `deploy_databricks()` will run this function the first time you use that function to deploy content to Posit Connect. 


## Usage
```r
 
requirements_write( 
  envname = NULL, 
  destfile = "requirements.txt", 
  overwrite = FALSE, 
  ... 
) 
```

## Arguments
|Arguments|Description|
|---|---|
| envname | The name of, or path to, a Python virtual environment. |
| destfile | Target path for the requirements file. Defaults to 'requirements.txt'. |
| overwrite | Replace the contents of the file if it already exists? |
| ... | Additional arguments passed to `reticulate::py_list_packages()` |



## Value
 No value is returned to R. The output is a text file with the list of Python libraries. 





```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
