---
title: "Starts and stops Spark Connect locally"
execute:
  freeze: true
---

```{r, eval=ecodown::examples_not_run()}
#| include: false
options("pillar.width" = 60)
library(sparklyr) 
library(dplyr)
```

*R/start-stop-service.R*

## spark_connect_service_start

## Description
 Starts and stops Spark Connect locally 


## Usage
```r
 
spark_connect_service_start( 
  version = "3.5", 
  scala_version = "2.12", 
  include_args = TRUE, 
  ... 
) 
 
spark_connect_service_stop(version = "3.5", ...) 
```

## Arguments
|Arguments|Description|
|---|---|
| version | Spark version to use (3.4 or above) |
| scala_version | Acceptable Scala version of packages to be loaded |
| include_args | Flag that indicates whether to add the additional arguments to the command that starts the service. At this time, only the 'packages' argument is submitted. |
| ... | Optional arguments; currently unused |



## Value
 It returns messages to the console with the status of starting, and stopping the local Spark Connect service. 





```{r, eval=ecodown::examples_not_run()}
#| include: false
spark_disconnect_all()
```
