---
title: "Sail"
format:
  html:
    toc: true
execute:
    eval: true
    freeze: true
editor:
  markdown:
    wrap: 72
---

```{r}
#| include: false

library(dplyr)
library(dbplyr)
library(sparklyr)
library(pysparklyr)

```

*Last updated: `r lubridate::date()`*

::: callout-warning
Sail support is experimental. It is only available in the development
version of `pysparklyr`.
:::

## Intro

[Sail](https://github.com/lakehq/sail) is a Spark Connect server written
in Rust. It does not need Java or a JVM. Sail runs the same Spark
DataFrame and SQL commands that Spark does, so `sparklyr` can talk to it
the same way it talks to [Spark Connect](/deployment/spark-connect.qmd).

Use Sail when you want to:

-   Run Spark code on your laptop without installing Java or Spark
-   Start a connection in a few seconds
-   Work with data that fits on a single machine

## How it works

`sparklyr` uses `reticulate` to call the Python `pyspark-client`
library. That library sends the commands to the Sail server over
*gRPC*. With a "local" connection, the Sail server runs inside your R
session.

::: {#fig-sail}
```{mermaid}
%%| fig-width: 10
%%| eval: true
flowchart LR
  subgraph rs[R session]
    subgraph r[R]
      sr[sparklyr]
      rt[reticulate]
    end
    subgraph ps[Python]
      pc[pyspark-client]
      sl[Sail server]
    end
  end
  sr <--> rt
  rt <--> pc
  pc <-- gRPC --> sl

  style rs  fill:#fff,stroke:#666,color:#000
  style r   fill:#fff,stroke:#666,color:#000
  style sr  fill:#fff,stroke:#666,color:#000
  style rt  fill:#fff,stroke:#666,color:#000
  style ps  fill:#fff,stroke:#666,color:#000
  style pc  fill:#fff,stroke:#666,color:#000
  style sl  fill:#fff,stroke:#666,color:#000
```

How `sparklyr` communicates with a local Sail server
:::

## Package installation

Install `sparklyr` from CRAN, and the development version of
`pysparklyr` from GitHub:

``` r
install.packages("sparklyr")
pak::pak("mlverse/pysparklyr")
```

## Python environment

`sparklyr` sets up a temporary Python environment for your R session by
using `uv`. This environment has the Python libraries that Sail needs.
You do not need to install anything else. Call `spark_connect()` and
`sparklyr` does the rest.

If `uv` is not available, use `install_sail()`. It creates a
persistent Python environment with these libraries:

-   `pysail`
-   The `pyspark-client` version that `pysail` needs
-   `rpy2`, which `spark_apply()` uses

``` r
pysparklyr::install_sail()
```

To install a specific Sail version, pass it in `version`:

``` r
pysparklyr::install_sail(version = "0.7")
```

## Connect

Set `method` to "sail". Use "local" for `master` to start a Sail server
inside your R session. Load `pysparklyr` before you connect:

```{r}
library(sparklyr)
library(pysparklyr)
library(dplyr)

sc <- spark_connect(master = "local", method = "sail")
```

The server uses a free port on your machine. `spark_disconnect()` stops
the server. The server also stops when the R session ends.

Now you can work with data in Sail. Sail does not cache tables in
memory, so set `memory` to `FALSE`:

```{r}
mtcars_tbl <- copy_to(sc, mtcars, memory = FALSE, overwrite = TRUE)

mtcars_tbl |>
  group_by(am) |>
  summarise(mpg = mean(mpg, na.rm = TRUE))
```

## Run R code

`spark_apply()` runs R code against each part of the data:

```{r}
mtcars_tbl |>
  spark_apply(nrow, group_by = "am", columns = "am double, x long")
```

With a "local" connection, the R code runs inside your R session, not
in a separate R process. This means:

-   If the R code crashes, it can end your R session
-   The R code can change objects in your global environment

```{r}
spark_disconnect(sc)
```

## Connect to a running Sail server

You can also connect to a Sail server that is already running. Pass the
server's address in `master`. The address uses the "sc://" protocol:

``` r
library(pysparklyr)

sc <- spark_connect(
  master = "sc://localhost:50051",
  method = "sail"
)
```

The Python environment of the server needs `pyspark-client`. To use
`spark_apply()`, the server also needs:

-   `rpy2`
-   R
-   The same Python version as your R session

See the [Sail
documentation](https://docs.lakesail.com/sail/latest/) to learn how to
start a Sail server.

## Limitations

Sail does not support some `sparklyr` features:

-   **Caching** - `copy_to()` and the `spark_read_*()` functions need
    `memory = FALSE`. `compute()` returns an error.
-   **Machine learning** - The `ml_*()` and `ft_*()` functions do not
    work.
-   **Tuning** - `tune_grid_spark()` does not work.
