---
title: "Sail"
format:
  html:
    toc: true
execute:
    eval: true
    freeze: true
editor:
  markdown:
    wrap: 72
---

```{r}
#| include: false

library(dplyr)
library(sparklyr)

# Sail writes its log straight to the process' stderr, so knitr does not
# see it. The `sail_log` chunk option sends stderr to a file while the chunk
# runs, and adds the file's lines to the chunk output
Rcpp::cppFunction(
  includes = "#include <unistd.h>\n#include <fcntl.h>",
  "int stderr_to_file(std::string path) {
    fflush(stderr);
    int saved = dup(2);
    int fd = open(path.c_str(), O_WRONLY | O_CREAT | O_TRUNC, 0644);
    dup2(fd, 2);
    close(fd);
    return saved;
  }"
)
Rcpp::cppFunction(
  includes = "#include <unistd.h>",
  "void stderr_restore(int saved) {
    fflush(stderr);
    dup2(saved, 2);
    close(saved);
  }"
)
sail_log <- new.env()
knitr::knit_hooks$set(sail_log = function(before, options) {
  if (before) {
    sail_log$file <- tempfile()
    sail_log$fd <- stderr_to_file(sail_log$file)
    return(invisible())
  }
  stderr_restore(sail_log$fd)
  lines <- cli::ansi_strip(readLines(sail_log$file, warn = FALSE))
  lines <- lines[lines != ""]
  if (length(lines) == 0) {
    return(invisible())
  }
  paste0("\n```\n", paste0("#> ", lines, collapse = "\n"), "\n```\n")
})

```

```{r}
#| include: false

# Remove when sparklyr 1.9.6 is on CRAN, since it loads pysparklyr for
# `method = "sail"`
library(pysparklyr)
```

*Last updated: `r lubridate::date()`*

::: callout-warning
Sail support is experimental. It is only available in the development
version of `pysparklyr`.

``` r
pak::pak("mlverse/pysparklyr")
```
:::

## Intro

[Sail](https://github.com/lakehq/sail) is a Spark Connect server written
in Rust. It does not need Java or a JVM. Sail runs the same Spark
DataFrame and SQL commands that Spark does, so `sparklyr` can talk to it
the same way it talks to [Spark Connect](/deployment/spark-connect.qmd). You
can connect to a remote Sail server that is already running, or to
a local Sail server on your machine.

## Get started

To start and work with a local Sail server, use `"sail"` as the `method`.
If you can use [`uv`](https://docs.astral.sh/uv/) on your machine,
`sparklyr` installs the Python libraries that Sail needs when you
connect. It then starts a local Sail server and connects you to it. You
do not need to do any other setup (a.k.a. **no Java needed!**).

```{r}
#| sail_log: true
library(sparklyr)

sc <- spark_connect(master = "local", method = "sail")
```

The server uses a free port on your machine. `spark_disconnect()` stops
the server. The server also stops when the R session ends.

## Python environment

If you cannot use `uv`, run `install_sail()` once, before you connect.
It creates a Python environment that stays on your machine. These are
the main libraries in the new Python environment:

-   `pyspark-client`, which is a thin version of `pyspark`
-   `pysail`, which `sparklyr` uses to start local Sail servers
-   `rpy2`, which runs the R code that `spark_apply()` sends

``` r
pysparklyr::install_sail()
```

After that, connect with `spark_connect()` as shown in [Get
started](#get-started). `sparklyr` finds and uses the new environment,
instead of having `uv` create a temporary one.

To install a specific Sail version, pass it in `version`:

``` r
pysparklyr::install_sail(version = "0.7")
```

## Work with data

Sail works with the same `sparklyr` and `dplyr` code that you use with
Spark. Copy a local data frame to Sail with `copy_to()`:

```{r}
library(dplyr)

mtcars_tbl <- copy_to(sc, mtcars, memory = FALSE)
```

Then use `dplyr` verbs. `sparklyr` turns them into Spark SQL, and Sail
runs the query:

```{r}
mtcars_tbl |>
  group_by(am) |>
  summarise(mpg = mean(mpg, na.rm = TRUE))
```

Use `collect()` to bring the results into R:

```{r}
mtcars_tbl |>
  filter(hp > 150) |>
  select(mpg, cyl, hp) |>
  collect()
```

You can also run SQL directly with `DBI`:

```{r}
DBI::dbGetQuery(sc, "SELECT cyl, COUNT(*) AS n FROM mtcars GROUP BY cyl")
```

## Run R code

`spark_apply()` runs an R function on each group of the data. Here,
`nrow()` counts the rows for each value of `am`. `columns` sets the
names and types of the result:

```{r}
mtcars_tbl |>
  spark_apply(nrow, group_by = "am", columns = "am double, x long")
```

::: callout-warning
With a `"local"` connection, the R code runs inside your R session, not
in a separate R process. This means:

-   If the R code crashes, it can end your R session
-   The R code can change objects in your global environment
:::

```{r}
#| include: false
spark_disconnect(sc)
```

## Connect to a running Sail server

You can also connect to a Sail server that is already running. Pass the
server's address in `master`. The address uses the "sc://" protocol.
Your machine still needs the Python environment from [Get
started](#get-started) or [Python environment](#python-environment):

``` r
sc <- spark_connect(
  master = "sc://localhost:50051",
  method = "sail"
)
```

The Python environment that runs the Sail server needs
`pyspark-client`. To use `spark_apply()`, the server also needs:

-   `rpy2`
-   R
-   The same Python version that your R session uses

See the [Sail
documentation](https://docs.lakesail.com/sail/latest/) to learn how to
start a Sail server.

## How it works

`sparklyr` uses `reticulate` to call the Python `pyspark-client`
library. That library sends the commands to the Sail server over
*gRPC*. With a `"local"` connection, `pysail` runs the Sail server, which
is written in Rust, inside your R session (@fig-sail). With a remote
connection, the commands go to a Sail server on another machine instead.

::: {#fig-sail}
```{mermaid}
%%| fig-width: 10
%%| eval: true
flowchart LR
  subgraph rs[R session]
    subgraph r[R]
      sr[sparklyr]
      rt[reticulate]
    end
    subgraph ps[Python]
      pc[pyspark-client]
      subgraph rust[Rust]
        sl[Sail server]
      end
    end
  end
  sr <--> rt
  rt <--> pc
  pc <-- gRPC --> sl

  style rs  fill:#fff,stroke:#666,color:#000
  style r   fill:#fff,stroke:#666,color:#000
  style sr  fill:#fff,stroke:#666,color:#000
  style rt  fill:#fff,stroke:#666,color:#000
  style ps  fill:#fff,stroke:#666,color:#000
  style pc  fill:#fff,stroke:#666,color:#000
  style rust fill:#fff,stroke:#666,color:#000
  style sl  fill:#fff,stroke:#666,color:#000
```

How `sparklyr` communicates with a local Sail server
:::

## Limitations

Sail does not support some `sparklyr` features:

-   **Caching** - `copy_to()` and the `spark_read_*()` functions need
    `memory = FALSE`. With `memory = TRUE`, they return an error.
    `compute()` also returns an error.
-   **Machine learning** - The `ml_*()` and `ft_*()` functions do not
    work.
-   **Tuning** - `tune_grid_spark()` does not work.
