---
title: "R interface for MLeap"
output:
  html_document:
    fig_width: 9
    fig_height: 5
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
aliases:
  /articles/deployment-connections.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, fig.height = 4, fig.width = 7, fig.align = 'center', cache = TRUE, eval = FALSE)
```

```{r, include = FALSE}
library(mleap)
```

**mleap** is a [sparklyr](http://spark.rstudio.com/) extension that provides an interface to [MLeap](http://mleap-docs.combust.ml/), which allows us to take Spark pipelines to production.

## Install `mleap`

**mleap** can be installed from CRAN via

```{r eval = FALSE}
install.packages("mleap")
```

or, for the latest development version from GitHub, using

```{r eval = FALSE}
devtools::install_github("rstudio/mleap")
```

## Setup

Once `mleap` has been installed, we can install the external dependencies using:

```{r eval = FALSE}
library(mleap)
install_mleap()
```

Another dependency of `mleap` is Maven.  If it is already installed, just point `mleap` to its location:

```r
options(maven.home = "path/to/maven")
```

If Maven is not yet installed, which is the most likely case, use the following to install it:

```r
install_maven()
```

## Create an MLeap Bundle

1. Start Spark session using `sparklyr`
    ```{r, message = FALSE}
    library(sparklyr)
    sc <- spark_connect(master = "local", version = "2.2.0")
    mtcars_tbl <- sdf_copy_to(sc, mtcars, overwrite = TRUE)
    ```
    
2. Create a fit an ML Pipeline    
    ```{r, message = FALSE}
    pipeline <- ml_pipeline(sc) %>%
      ft_binarizer("hp", "big_hp", threshold = 100) %>%
      ft_vector_assembler(c("big_hp", "wt", "qsec"), "features") %>%
      ml_gbt_regressor(label_col = "mpg")
    
    pipeline_model <- ml_fit(pipeline, mtcars_tbl)
    ```

3. A transformed data frame with the appropriate schema is required for exporting the Pipeline model
    ```{r}
    transformed_tbl <- ml_transform(pipeline_model, mtcars_tbl)
    ```

4. Export the model using the `ml_write_bundle()` function from `mleap`
    ```{r}
    model_path <- file.path(tempdir(), "mtcars_model.zip")
    ml_write_bundle(pipeline_model, transformed_tbl, model_path)
    ```

5. Close Spark session
    ```{r}
    spark_disconnect(sc)
    ```

At this point, we can share `mtcars_model.zip` with the deployment/implementation engineers, and they would be able to embed the model in another application. See the [MLeap docs](http://mleap-docs.combust.ml/) for details.

## Test the `mleap` bundle

The `mleap` package also provides R functions for testing that the saved models behave as expected. Here we load the previously saved model:

```{r}
model <- mleap_load_bundle(model_path)
model
```

To retrieve the schema associated with the model use the `mleap_model_schema()` function

```{r}
mleap_model_schema(model)
```

Then, we create a new data frame to be scored, and make predictions using the model:

```{r}
newdata <- tibble::tribble(
  ~qsec, ~hp, ~wt,
  16.2,  101, 2.68,
  18.1,  99,  3.08
)

# Transform the data frame
transformed_df <- mleap_transform(model, newdata)
dplyr::glimpse(transformed_df)
```
